Best Practices for Alchemical Free Energy Calculations: v\versionnumber

### 2020-01-10 paper/manuscript.tex
updating section on different sampling schemes

\subsubsection{What different sampling schemes exist and which one should I use?}
\todo[inline, color={green!20}]{ASJSM: I'll expand on this}
\ref{fig:fig_sampling_scheme} A:\cite{hedges2019biosimspace, song2019using } B\cite{aldeghi2015accurate, wang2015accurate,jiang2019computing} C:\cite{li2007simulated, tan2017optimally} D:\cite{aldeghi2018accurate}
\begin{figure}
    \includegraphics[width=0.95\columnwidth]{figures/fig8_sampl_scheme/Figure.pdf}
    \caption{\textbf{Four sampling strategies available in different software packages.} \textbf{A}: Multiple replicas in parallel at different lambda states. \textbf{B}: Hamiltonian replica exchange scheme. \textbf{C}: Single replica scheme sampling from all $\lambda$ states. \textbf{D}: Non-equilibrium sampling scheme.}
    \label{fig:fig_sampling_scheme}
\end{figure}

>>>>

\subsubsection{What different sampling schemes exist and which one should I use?}
With all AFE simulations having the requirement of sampling from different sets of $\lambda$ states in common different approaches have been designed. Fig.~\ref{fig:fig_sampling_scheme} illustrates the four most common schemes used. The simplest approach is defining a set of fixed $\lambda$ values and then run independent simulations at each of the intermediate $\lambda$ values, see fig.~\ref{fig:fig_sampling_scheme}(A). This type of scheme is currently used for AMBER TI calculations~\cite{song2019} and for BioSimSpace~\cite{hedges2019biosimspace}. A slightly more complex approach is allowing replica mixing, meaning that each independent $\lambda$ simulation is attempted to be exchanged with a neighbouring $\lambda$ replica. This is based on ideas of Monte Carlo simulations of spin glasses by Swendsen and Wang~\cite{wendsen1986replica}. Using a Metropolis Hastings based acceptance criterion for exchanges means that the generated ensemble of all replicas is still sampling from the Boltzmann distribution and has been used in many different contexts for molecular simulations~\cite{sugita2000multidimensionala,sugita1999replicaexchangea, woods2003developmenta, jiang2010free}. The basic idea of the replica exchange scheme is shown in fig.~\ref{fig:fig_sampling_scheme}(B). It is supported in various software packages that provide AFE implementations, such as GROMACS~\cite{aldeghi2015accurate}, FEP+~\cite{wang2015accurate}, and NAMD~\cite{jiang2019computing}. A third approach borrows ideas from simulated tempering~\cite{marinari1992simulateda}. In this scheme a single replica rapidly explores all of $\lambda$ space by optimally working out weights that allow switching between different intermediate $\lambdas$, as seen in fig.~\ref{fig:fig_sampling_scheme}(C) and also referred to as self adjusted mixture sampling~\cite{lyubartsev1992newa, li2007simulated, tan2017optimally} and while promising, has so far only been supported in~\cite{andrearizzi2019choderalab}. The last approach available in conjunction with GROMACS makes use of non-equilibrium simulations~\cite{aldeghi2018accurate}. In this approach, only end state $\lambda$ replicas ($\lambda$=0, $\lambda=1$) are simulated at equilibrium intermediate information is generated from non-equilibrium simulations. A schematic of this approach is shown in fig.~\ref{fig:fig_sampling_scheme}. 
\ref{fig:fig_sampling_scheme} A:\cite{hedges2019biosimspace, song2019using } B\cite{aldeghi2015accurate, wang2015accurate,jiang2019computing} C:\cite{li2007simulated, tan2017optimally} D:\cite{aldeghi2018accurate}
\begin{figure}
    \includegraphics[width=0.95\columnwidth]{figures/fig8_sampl_scheme/Figure.pdf}
    \caption{\textbf{Four sampling strategies available in different software packages.} \textbf{A}: Multiple replicas in parallel at different lambda states. \textbf{B}: Hamiltonian replica exchange scheme. \textbf{C}: Single replica scheme sampling from all $\lambda$ states. \textbf{D}: Non-equilibrium sampling scheme.}
    \label{fig:fig_sampling_scheme}
\end{figure} 
The best practice recommendation, is to use replica exchange type sampling schemes (fig.~\ref{fig:fig_sampling_scheme}(B)), or in absence of their availability and when looking at systems with fast mixing times parallel replica schemes are acceptable (fig.~\ref{fig:fig_sampling_scheme}(A)). Single replica schemes and non-equilibrium schemes are not as established yet, but are very promising.
